Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-11-19 manuscript_v2_noiseSim.tex
updates to facula and spot sections

\usepackage{afterpage}

@@

For the simulations discussed below, a star similar to the Sun was modelled with a solar disc of one solar radius seen equator-on, and a stellar rotational period set to 25.0 days.
The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}. {\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
{\bf{ We consider for our simulations SNR=100.}}

@@

Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are {\bf{weaker}} than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of {\bf{$R$=-0.11, -0.55 and -0.81}}, respectively. 
%
{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$), but the correlation between FWHM and N mean RV is the weakest ($R=0.47$).}} 
This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters. Therefore, the SN parameters may better probe stellar activity. 
We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec.~\ref{sec:4} with real observations.

@@

The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a {\bf{$R^2$ larger than $0.98$.}}
%In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
%We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to about 1.2 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 7.07 \ms to 0.88 \ms and for SN mean RV are 5.9 \ms to 0.88 \ms.}}
When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e. a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}. Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant. When using the Normal variables, the parameters $\beta_{3}$ and $\beta_{4}$ are not statistically helpful for the correction.}}

@@

Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates of the CCF barycenter (i.e. SN mean RV, SN median RV and N mean RV). {\bf{The correlation between $\gamma$ and SN median RV and the correlation between the BIS SPAN and N mean RV are the strongest ($R=-0.81$) followed by the $\gamma$ - SN mean RV correlation ($R=-0.76$).}} 
The correlations between the width and the CCF barycenter are more circular and no substantial correlation is observed. 
Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.

@@

As before, the original RV estimates are corrected using Eq.~\eqref{eq:RV:correction}. 
The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}. 
{\bf{In this case the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8}}.

%In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to about 3.04 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 5.85 \ms to 2.74 \ms and for SN mean RV are 5.27 \ms to 2.74 \ms.}}
When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.}}
%This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.

>>>>

\usepackage{afterpage}
\usepackage{ulem}

@@

For the simulations discussed below, a star similar to the Sun was modelled with a solar disc of one solar radius seen equator-on, and a stellar rotational period set to 25.0 days.
The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}. {\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
{\bf{ We consider an SNR=100 for our simulations.}}

@@

Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are {\bf{weaker}} than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of {\bf{$R$=-0.11, -0.55 and -0.81}}, respectively. 
%
{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$).  The correlation between FWHM and N mean RV is the weakest ($R=0.47$), and the correlation between FWHM and SN mean RV is the strongest ($R=0.92$).}} 
This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters. 
{\bf Therefore, the SN parameters may better probe stellar activity that induces changes in the FWHM.}
We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec.~\ref{sec:4} with real observations.

@@

The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a {\bf{$R^2$ larger than $0.98$.}}
%In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
%We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to {\color{red}1.02} \ms after correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 7.07 \ms to 0.88 \ms and for the SN mean RV are 5.9 \ms to 0.88 \ms.}}
When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e. a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by {\color{red} \bf an additional 14.5 -} {\bf{15\%}} {\color{red} \bf [I think we should emphasize the proposed correction is in addition to the usual correction, and it seems the range of improvement is actually 14.5-15\%]}. Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant. When using the Normal variables, the parameters $\beta_{3}$ and $\beta_{4}$ are not statistically helpful for the correction.}}

@@

Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates of the CCF barycenter (i.e. SN mean RV, SN median RV and N mean RV). {\bf{The correlation between $\gamma$ and SN median RV and the correlation between the BIS SPAN and N mean RV are the strongest ($R=-0.81$) followed by the $\gamma$ - SN mean RV correlation ($R=-0.76$).}} 
The correlations between the width and the CCF barycenter are more circular and no substantial correlation is observed. 
Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters. {\color{red} \bf I'm not sure the previous statement is correct anymore - the only correlations strong with the SN variables is described has having ``no substantial correlation'' in the previous statement...I suggest we delete the previous sentence, or revise to make it correct.]}

@@

As before, the original RV estimates are corrected using Eq.~\eqref{eq:RV:correction}. 
The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}. 
%{\bf{In this case the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8}}. 
{\bf The $R^2$ values for the linear combination are between 0.72 and 0.78, which are not as strong as the setting with a facula.}

%In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to 3.04 \ms after  correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 5.85 \ms to 2.74 \ms and for the SN mean RV are 5.27 \ms to 2.74 \ms.}}
When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf \color{red} and additional 5.3 - 5.8\% ]} \sout{\bf{6 \%}}.
The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that captures the interaction between the width and the asymmetry of the CCF.}}
%This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
